\Title

### 2020-04-07 manuscript/manuscript.tex
Finish introduction with a motivation paragraph
Added some more references for strategies for accelerating the EQL
processing. Need to add text about them all.

% Define title, authors, affiliations and DOI
% ===========================================
\newcommand{\Title}{
    A better strategy for interpolating gravity and magnetic data
}
\newcommand{\Author}{
    S.R. Soler,
    L. Uieda
}
\newcommand{\AuthorAffil}{
    {\large
        S.R. Soler$^{1,2}$,
        L. Uieda$^{3}$
    }
    \\[0.4cm]
    {\small $^{1}$CONICET, Argentina (santiago.r.soler@gmail.com)} \\
    {\small $^{2}$Instituto Geofísico Sismológico Volponi, UNSJ, Argentina} \\
    {\small $^{3}$University of Liverpool} \\

@@

Measurements of anomalies in potential fields, like gravity disturbances and
total-field magnetic anomalies, are widely used in geophysical exploration for
their relatively low cost of acquisition.
These data can be surveyed using ground, airborne, shipborne, or satellite
systems.
In ground surveys, the data are often gathered following
irregular paths or networks along the surface of the terrain, leading to highly
variable elevations in mountainous regions.
On airborne surveys, the data are gathered along flight lines, producing a
large number of measurements concentrated along almost straight lines.
In surveys that drape the topography, the height of measurement could change
dramatically because of the vertical movement of the aircraft.
Processing of the data often involves interpolation onto a regular grid at
constant height, both to improve visualization for interpretation purposes as
well as to prepare the data for further processing and modelling (e.g.,
reduction-to-the-pole, derivative calculations, upward continuation, Euler
deconvolution),

Several methods exist in the literature for interpolation in two dimensions,
for example continuous curvature splines in tension \citep{smith1990},
biharmonic (thin-plate) splines \citep{sandwell1987}, and kriging.
These general-purpose methods have limitations when it comes to interpolating
potential field data:
(i) they are not able to take into account the variable height of the
observation points;
(ii) the interpolating functions are not necessarily harmonic functions, which
is the underlying assumption behind many processing techniques
(e.g., upward continuation and vertical derivatives).

One of the most widely used methods for interpolating gravity and magnetic data
is the equivalent sources technique (also known as equivalent layer, radial
basis functions or Green's functions interpolation).
It consists in estimating a source distribution that produces the same field as
the one measured and using this estimate to predict new values.
\citet{dampney1969} was the first to introduce the equivalent source technique.

The EQL can be used for interpolation of potential field data
\citep{cordell1992, cooper2000}.
It has been also used for applying a reduction to the pole to magnetic data
\citep{guspi2009, silva1986, emilia1973, nakatsuka2006} or an upward
continuation (cite).

The most widely used source distribution is a set of point sources.
The potential field of point sources is easy to compute.
\citet{barnes2011} make use of prisms.
How to locate these point masses?
Existing approaches:
(i) one point source beneath each observation point at a constant depth (cite),
(ii) one point source beneath each observation point at a depth proportional to
the distance to its nearest data points (cite),
(iii) a regular grid of sources \citep{barnes2011}.

We want to find out which distribution of sources produces the best
interpolations.

>>>>

% Define title, authors, affiliations and DOI
% ===========================================
\newcommand{\Title}{
    A better strategy for interpolating gravity and magnetic data
}
\newcommand{\Author}{
    S.R. Soler,
    L. Uieda
}
\newcommand{\AuthorAffil}{
    {\large
        S.R. Soler$^{1,2}$,
        Leonardo Uieda$^{3}$
    }
    \\[0.4cm]
    {\small $^{1}$CONICET, Argentina (santiago.r.soler@gmail.com)} \\
    {\small $^{2}$Instituto Geofísico Sismológico Volponi, UNSJ, Argentina} \\
    {\small $^{3}$Department of Earth, Ocean and Ecological Sciences, School of Environmental Sciences, University of Liverpool, UK} \\

@@

Measurements of anomalies in potential fields, like gravity disturbances and
total-field magnetic anomalies, are widely used in geophysical exploration for
their relatively low cost of acquisition.
These data can be surveyed using ground, airborne, shipborne, or satellite
systems.
In ground surveys, the data are often gathered following
irregular paths or networks along the surface of the terrain, leading to highly
variable elevations in mountainous regions.
On airborne surveys, the data are gathered along flight lines, producing a
large number of measurements concentrated along almost straight lines.
In surveys that drape the topography, the height of measurement could change
dramatically because of the vertical movement of the aircraft.
Processing of the data often involves interpolation onto a regular grid at
constant height, both to improve visualization for interpretation purposes as
well as to prepare the data for further processing and modelling (e.g.,
reduction-to-the-pole, derivative calculations, upward continuation, Euler
deconvolution).

Several methods exist in the literature for interpolation in two dimensions,
for example continuous curvature splines in tension \citep{smith1990},
biharmonic (thin-plate) splines \citep{sandwell1987}, and kriging.
These general-purpose methods have limitations when it comes to interpolating
potential field data:
(i) they are not able to take into account the variable height of the
observation points and
(ii) the interpolating functions are not necessarily harmonic functions, which
is the underlying assumption behind many processing techniques
(e.g., upward continuation and vertical derivatives).

A widely used method for interpolating gravity and magnetic data
is the equivalent source technique (also known as equivalent layer, radial
basis functions, or Green's functions interpolation), first introduced by
\citet{dampney1969}.
It consists in fitting a model of point sources to the data and using this
model to predict new data values.
Besides interpolation, equivalent sources have been used for
reduction-to-the-pole of magnetic data
\citep{guspi2009, silva1986, emilia1973, nakatsuka2006}, upward
continuation (CITATION NEEDED), and merging datasets (CITATION NEEDED).

Many variants of the equivalent source technique have been proposed.
The key factors that vary between them are: (i) the type of source, (ii)
the location of the sources, and (iii) the solution strategy.
The type of source is most commonly a point mass (for gravity) or dipole (for
magnetics) (CITATION NEEDED).
However, an inverse distance function $1/r$ (CITATION NEEDED),
right-rectangular prisms (CITATION NEEDED:
one by the simpeg group and one for magnetic data integration),
and tesseroids \citep{bouman2016} have also been used successfully.
The sources are often distributed on a regular grid at a constant depth (e.g.,
CITATION NEEDED) or placed beneath each data point (e.g., CITATION NEEDED).
The model is usually estimated through damped least-squares, which imposes a
heavy computational load when the number of data points is large (e.g.,
airborne and satellite surveys).
Other solution strategies have been proposed to attempt to reduce this load and
make the use of equivalent sources feasible.
\citet{mendonca1994} blablabla.
\citet{leao1989} blablabla.
\citet{li2010} blablabla.
\citet{barnes2011} blablabla.
\citet{oliveira2013} blablabla.
\citet{siqueira2017} blablabla.
\citet{jirigalatu2019} blablabla.
Many other techniques have been proposed, more so than could be included here.

In the present study, we will evaluate the impact of different source
distributions, both horizontally and vertically, on the performance of
equivalent source interpolation.
Vertically, the sources can be located: (i) at a constant depth, (ii) at a
depth proportional to the height of observations, and (iii) at a depth
proportional to the median distance to adjacent data points.
The horizontal source distribution strategies are: (i) regular grid, (ii)
beneath data point, (iii) on the median location of data points inside spatial
blocks. The latter is a novel method while the others have been used in some
form in the past.
